---
title: "Project A Summary based on the Proposals"
---

This page was last updated: `r Sys.time()`.

```{r setup, include=FALSE}
knitr::opts_chunk$set(comment = NA)
```

# States Selected

We have 55 projects. 

- 26 projects use four states, 18 use 5 states, and 11 use 6 states.
- In total, we have 260 "states" in use.
- The states which we "permitted" you to use that no one chose were:
    - Kansas (104 counties), Kentucky (120), North Dakota (48), Nebraska (80) and Oklahoma (77).
- States (and DC) you were not permitted to use (because they have < 12 counties) were:
    - Connecticut (8 counties), Delaware (3), Hawaii (4), New Hampshire (10), Rhode Island (5) and Washington DC (1).
- Identical states were chosen by two different groups in two cases... 
    - Two projects use Ohio, Indiana, Michigan and Pennsylvania (330 counties, 4 states) 
    - Two projects use Ohio, Illinois, Indiana and Michigan (365 counties, 4 states)

Here's a graph of the states used at least once, excluding Ohio, which was used in all 55 projects:

```{r, echo = FALSE, message = FALSE, fig.height = 10, fig.width = 5}
library(tidyverse)
temp <- read_csv("proj2020.csv")

temp <- temp %>% filter(projects > 0, state != "Ohio") %>%
    arrange(desc(state))

ggplot(temp, aes(x = projects, y = reorder(state, projects))) +
    geom_label(aes(label = projects)) + theme_bw() +
    labs(title = "States used in 1 or more Project A",
         subtitle = "55 Fall 2020 431 Projects, all of which used Ohio",
         y = "")
```

# Variables Selected

No two projects selected the same five variables.

## Most Common Selections

Teams selected 56 of the 107 possible variables.

- The most common variable selected was `v063` (Median household income), selected in 23 of the 55 projects, but only once as an outcome.
- `v023` (Unemployment) is used in 14 projects (but never as the outcome)
- `v009` (Adult smoking) is used in 13 (only 2 times as the outcome)
- `v147` (Life expectancy) is also used in 13 (12 times as the outcome)
- `v042` (Poor mental health days) is used in 12 (6 times as the outcome)
- `v085` (Uninsured) is used in 10 (once as the outcome)
- Other common choices included:
    - `v011` (Adult obesity), `v139` (Food insecurity), `v143` (Insufficient sleep) and `v145` (Frequent mental distress) were each used in 9 projects,
    - `v021` (High school graduation), `v044` (Income inequality), `v049` (Excessive drinking) and `v070` (Physical inactivity) were each used in 8 projects,
    - `v001` (Premature death), `v062` (Mental health providers) and `v069` (Some college) were each used in 7
    - `v037` (Low birthweight), `v161` (Suicides) were each used in 6
    - `v002` (Poor or fair health), `v014` (Teen births), and `v043` (Violent crime) were each used in 5 projects

## Outcome

- 12 of 55 projects selected `v147` (Life expectancy) as their outcome
- 6 more selected `v001` (Premature death), and 6 also selected `v042` (Poor mental health days)
- 5 selected `v161` (Suicides)
- 4 selected `v037` (Low birthweight)
- 3 selected `v127` (Premature age-adjusted mortality)
- 2 selected `v002` (Poor or fair health), `v009` (Adult smoking), `v043` (Violent crime), and `v060` (Diabetes prevalence)
- while the other 11 projects used something no one else did.

## Most Common Quantitative Predictors

- 10 projects used `v063` (Median household income)
- 7 projects used `v049` (Excessive drinking)
- 6 projects used `v085` (Uninsured) and 6 used `v145` (Frequent mental distress)
- 5 projects used `v009` (Adult smoking), `v021` (High school graduation), `v023` (Unemployment), `v139` (Food insecurity) and `v143` (Insufficient sleep)

## Most Common Binary Predictors

- 7 of 55 projects selected `v023` (Unemployment) to use for a binary categorical predictor
- 5 used `v063` (Median household income)
- 4 used `v009` (Adult smoking) and 4 used `v011` (Adult obesity)

## Most Common Multi-Categorical Predictors

36 projects split into 3 categories, 10 into 4 and just 9 into 5.

- 7 of 55 projects chose `v063` (Median household income)
- 3 used `v043` (Violent crime), `v069` (Some college), `v139` (Food insecurity) and 3 used `v145` (Frequent mental distress)

# Titles of Your 55 Projects

My favorite title at the moment of these 55 is bolded. Tomorrow, I'll probably like one of the other ones better.

If you're considering a revision to your title, especially after you've completed the analyses and have something more substantial to say, I encourage you to think about whether you need words that appear many times in the other titles here, or whether there's a more effective way to entice your audience and stand out.

1. A Look into Ohio, Louisiana, Florida, and Vermont
2. An Exploration of the County Heath Rankings Data
3. Analysis of Adverse Mental Health Outcomes as a Reflection of Access to Mental Health Providers
4. Analysis of County-Level Health Indicators in Five US States
5. Analysis Of Math Test Scores in the U.S.
6. Analyzing the Factors for Premature Death
7. Assessing Poor Mental Health Days
8. Assessment and Comparing Suicidal Risk Factors in Ohio and Three Other States
9. Association of Air pollution with Poor Health Outcomes in Five States in the Great Lakes Region
10. Behavioral factors and their link with a life expectancy
11. Building a Predictive Model for Mental Health in Counties
12. CHR Data for Estimation of Birth Weight Outcomes
13. **Contributors to Violent Crime in 2020 U.S. Presidential Election Swing States**
14. Diabetes Prevalence in the 2020 County Health Rankings
15. Effect of Health Factors of a 20-Something Millenial on Life Expectancy
16. Examining factors potentially affecting low birthweight rates in six states
17. Exploration of Association of Social & Economic Factors with Health Behaviors in OH, CA, GA, SD and NJ
18. Exploration of factors potentially associated with premature death among the top ranked states for premature deaths plus Ohio
19. Exploring Life Expectancy in Midwestern US Counties
20. Factors Associated with Adult Smoking Prevalence in Four US States
21. Factors associated with violent crime across counties in OH, CA, CO, TN, & PA
22. Factors Contributing to Physical Inactivity
23. Five State Analysis of Premature Death Associations Using Community Health Rankings Data
24. Health Outcomes in the 2020 Presidential Race Battleground States
25. Health Status of Four US States
26. Impact of Health Factors on Life Expectancy in Rust Belt States
27. Impact of Public Health Factors on Low Birthweight
28. Influences on Life Expectancy in Counties in OH, NY, NJ, and CO
29. Interrogation health behaviors and life expectancy relationship:  evidence from four census region state candidates
30. Investigating Poor Mental Health Days in Select Rust Belt States
31. Modeling Preventable Hospitalization Rates at the County Level
32. Physical and Mental Health in the US
33. Poor Health May be Linked to Living in Disadvantaged Areas
34. Poor mental health: Predictors and Outcomes
35. Predicting Adult Obesity Rate in US Counties
36. Predicting adult smoking rates using mental, physical, and financial stress
37. Predicting Income Levels in Counties in the Midwest with Indicators of Community Wellness
38. Predicting life expectancy from health and social indicators
39. Predictors of Access to Mental Health Care in Counties in Six U.S. States
40. Predictors of health outcomes across counties in OH, MN, WA, and UT
41. Predictors of Life Expectancy
42. Predictors of poor perinatal outcomes in the American Midwest
43. Premature death rates analysis in four US states
44. Premature mortality across US states
45. Quality of Life and Premature Death
46. Relationship between County Life Expectancy and Health Behaviors
47. Sleep Duration, Motor Vehicle Deaths, Household Income and the Relation to Suicide in Five States
48. Socio-Economic Barriers Limit Access to Appropriate Health Care Coverage
49. Socioeconomic and Lifestyle Factors in Suicide Rates
50. Studying Life Expectancy as a Measure of Health Outcomes in 6 Representative States and Their Counties in the United States
51. The Association Between Dietary and Physical Health Behaviors, Socioeconomic Status and Life Expectancy Among 5 US States
52. The effect of Socio-economic factors and Health Behaviors on Life Expectancy across 5 States
53. The impact of various health and social factors in diabetes prevalence
54. The Relationship Between Measures of Despair and Premature Death in Midwestern States
55. What factors contribute to Suicide Rate

